---
title: "SixSeven Results "
author: "Elika"
output: html_document
---

#Talk, you're on camera


```{r read in data, comment=F, message=F, hide = T, warning = F, echo = F}
#06 and 07 aud vid comparison
source("sixseven_data_aggregation.R")
source("wilcoxon_corrs_sixseven.R")
source("sixseven_figure_code.R")
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
#to do's: add and format tables wherever they're indicated; 
# create figure legends, and tinker to make sure figures render at reasonable size/ratios
# refer to figures and tables with \@ref(fig:chunk-name) for figures * \@ref(tab:chunk-name) for tables, bookdown style
# add the table from the googledoc version, maybe? or just once it's finalized, take a pic of it and add as figure?
```
#Results 
##Analysis Plan
Based on the coding scheme above, we derived count (n=12) and proportional (n=10) measures from the annotations in each file. See table XX. We then aggregated the data at the recording level, generating derived count and proportion values for each child (n=44), for each recording-type (audio, video), for each month (six, seven). We also normalized the count measures by recording length to allow direct comparison across daylong and hourlong recordings (further details below). We initially created multi-level models, with each of the 22 measures as the dependent variable,  recording-type (audio/video) and month (six/seven) as fixed effects and participant as a random effect (i.e. dv ~ recording_type + month + (1|subj)). Month was not a significant predictor in any of the 22 models; recording-type was in 17/22 models. However, since many of the models showed structured (generally funnel-shaped) residuals that limited interpretation across measures, we instead adopted a simple set of nonparametric analyses. 

For all recording type and month comparisons, we look at whether our measures *differed* significantly (by two-tailed, paired Wilcoxon Test), and *correlated* significantly (by Kendall Rank Correlation) across the given groups. This approach lets us compare, for instance, whether the proportion of declaratives is indistinguishable in our audio and video recordings independently of whether these values are correlated across recording types. We applied Holm’s p-value adjustment for multiple comparisons (Holm, 1979), for each set of Wilcoxon and Kendall tests. For instance, comparing the 12 count measures for month six versus month seven within audio recordings by Wilxocon test is one 'set'; given our analysis plan of 2(count or proportional) x 2(audio or video) x 2 (six or seven month) x 2(Wilcoxon Test or Kendall correlation), there are 15 further sets to which this p-value adjustment was applied. 

```{r wilcoxon_count_withinAV_sixsev, echo=F, message = F, warning = F}

vidmode <- getmode(round(vidtime$total_min)) #rounding to the minute 1st
cas_mintau <- ifelse(sum(cas$pval_adj>0),round(min(cas$estimate),2),"FIXTHIS")
cas_maxtau <- ifelse(sum(cas$pval_adj>0),round(max(cas$estimate),2),"FIXTHIS")
cas_taup <- ifelse(sum(cas$pval_adj>0.05)==0, "all adjusted-p<.05","FIXTHIS")
was_ps <- ifelse(sum(was$pval_adj<0.05)==0, "all adjusted-p>.05","FIXTHIS")
cvs_nonsigpval <- ifelse(filter(cvs, comp=="cv_r")$pval_adj>.05,"adjusted-p>.05","FIXTHIS")
cvs_sigpval <- ifelse(sum(filter(cvs, comp!="cv_r")$pval_adj)>0,"all adjusted-p<.05","FIXTHIS")
cvs_numsigps <- length(subset(cvs, pval_adj<.05)$estimate)
cvs_mintau <- round(min(subset(cvs, pval_adj<.05)$estimate),2)
cvs_maxtau <- round(max(subset(cvs, pval_adj<.05)$estimate),2)
wvs_ps <- ifelse(sum(wvs$pval_adj<0.05)==0, "all adjusted-p>.05","FIXTHIS")

```

##Derived Counts, Month 6 vs. 7
We first analyzed the 12 derived count measures in month six versus seven, by recording-type. Across children, all 12 derived count audio measures correlated significantly month-to-month (Kendall’s tau ranged from `r cas_mintau` - `r cas_maxtau`, `r cas_taup`), and did not significantly differ by month (`r was_ps`). Eleven of twelve video measures correlated significantly month-to-month (Kendall’s taus ranged from `r cvs_mintau` - `r cvs_maxtau`, `r cvs_sigpval`), except number of reading tokens (`r cvs_nonsigpval`). For video too no derived count measures varied significantly from six to seven months (`r wvs_ps`.) Thus, within recording type, the count-based metrics of the object words infants heard were statistically equivalent in month six and seven, and correlated significantly within children month-to-month (except 1/24 correlations). This suggests that parents are likely behaving relatively naturally during recordings, or are adjusting their behavior as a function of our observations to an extremely consistent degree. 

```{r gr_derived_counts_67_diff, echo = F, fig.height = 8, warning = F}
gr_countvals_long

```
```{r gr_derived_counts_67_corr, echo = F, fig.width=12, fig.height=3, warning = F}

gr_count_cor_67_facetav

```

```{r lengths, echo = F, warning = F, message = F}
audmode <- getmode(audtime$total_min)
audmode_nosil_hr <- round(getmode(audtime$tot_nosil/60),1)
aud_nosilM <- round(mean(audtime$tot_nosil)/60,2)
aud_nosilSD <- round(sd(audtime$tot_nosil)/60,2)
aud_nosilmin <- round(min(audtime$tot_nosil)/60,2)
aud_nosilmax <- round(max(audtime$tot_nosil)/60,2)

vidM_SD_R <- paste(round(mean(vidtime$total_min),2), ", SD=",round(sd(vidtime$total_min),2),
                   ", R=",min(vidtime$total_min), "-", max(vidtime$total_min)," min", sep = "")
audM_SD_R <- paste(round(mean(audtime$total_hr),2), ", SD=",round(sd(audtime$total_hr),2),
                   ", R=",min(audtime$total_hr), "-", max(audtime$total_hr)," hr", sep = "")
audM_SD_Rmin <- paste(round(mean(audtime$total_min),2), ", SD=",round(sd(audtime$total_min),2),
                   ", R=",min(audtime$total_min), "-", max(audtime$total_min)," min", sep = "")

audnosilM_SD_R <- paste(aud_nosilM*60, ", SD=",aud_nosilSD*60,", R=",aud_nosilmin*60, "-", aud_nosilmax*60, " min", sep = "")
```

##Derived Counts, Audio vs. Video-recordings
We next assessed how quantity of input scaled between  hour-long video recordings and daylong audio recordings. Modally, videos were an hour (`r vidmode` min); audio-recordings were 16 hours (`r audmode` min), the maximum capacity of the LENA device. However, there was some variability across recordings (video: *M*=`r vidM_SD_R`; audio *M*=`r audM_SD_Rmin`).  While it can be difficult to ascertain from audio alone when the children were napping, by removing the 'silent' portions of the recordings (see Methods), we can estimate an upper-limit on their awake (i.e. non-silent) time (Mode = `r audmode_nosil_hr`, *M* = `r audnosilM_SD_R` ). This is in line with established norms for 6–8-month-olds in the US (Mandel et al, 2010), which report the average amount of sleep is 3 hours during the day, and 10 hours during the night. Thus, 16 hours of recording beginning when the child wakes up should capture ~11 daytime waking hours, in line with our silence demarcations. Infants were awake during video recordings (save one infant, who fell asleep before the recording hour ended; that video was stopped at sleep onset).


```{r scaling examination, echo = F, warning = F, message = F}
#count comparison by min
#avg a-boost, removing any NAs
aboost_mean <- sixseven_spreadAV %>% 
  dplyr::select(subj, month, a_total_min, a_tot_nosilsk, a_tot_nosil,v_total_min,
                a_numtypes, v_numtypes, a_numtokens, v_numtokens, a_numspeakers, v_numspeakers,a_MOT, v_MOT, a_FAT, v_FAT, a_d, v_d, a_q, v_q, a_i, v_i, a_s, v_s, a_r, v_r, a_n, v_n, a_y_op, v_y_op) %>% 
  mutate_if(is.numeric, funs(na_if(., 0)))  %>% 
  group_by(month) %>% 
  summarise(
    aboost_min = mean(a_total_min/v_total_min),
    aboost_awakemin = mean(a_tot_nosil/v_total_min),
    aboost_types =mean(a_numtypes/v_numtypes, na.rm=T),
    aboost_tokens = mean(a_numtokens/v_numtokens, na.rm=T),
    aboost_speakers = mean(a_numspeakers/v_numspeakers, na.rm=T),
    aboost_MOT = mean(a_MOT/v_MOT, na.rm=T),
    aboost_FAT = mean(a_FAT/v_FAT, na.rm=T),
    aboost_d = mean(a_d/v_d, na.rm=T),
    aboost_q = mean(a_q/v_q, na.rm=T),
    aboost_i = mean(a_i/v_i, na.rm=T),
    aboost_s = mean(a_s/v_s, na.rm=T),
    aboost_r = mean(a_r/v_r, na.rm=T),
    aboost_n = mean(a_n/v_n, na.rm=T),
    aboost_op = mean(a_y_op/v_y_op, na.rm=T),
    comp = "mean_aboost") %>% 
  mutate_if(is.numeric, funs(round(., 2)))
# sd of a_boost, removing NAs
aboost_sd<- sixseven_spreadAV %>% 
  dplyr::select(subj, month, a_total_min, a_tot_nosilsk, a_tot_nosil,v_total_min,
                a_numtypes, v_numtypes, a_numtokens, v_numtokens, a_numspeakers, v_numspeakers,a_MOT, v_MOT, a_FAT, v_FAT, a_d, v_d, a_q, v_q, a_i, v_i, a_s, v_s, a_r, v_r, a_n, v_n, a_y_op, v_y_op) %>% 
  mutate_if(is.numeric, funs(na_if(., 0)))  %>% 
  group_by(month) %>% 
  summarise(
    aboost_min = sd(a_total_min/v_total_min),
    aboost_awakemin = sd(a_tot_nosil/v_total_min),
    aboost_types =sd(a_numtypes/v_numtypes, na.rm=T),
    aboost_tokens = sd(a_numtokens/v_numtokens, na.rm=T),
    aboost_speakers = sd(a_numspeakers/v_numspeakers, na.rm=T),
    aboost_MOT = sd(a_MOT/v_MOT, na.rm=T),
    aboost_FAT = sd(a_FAT/v_FAT, na.rm=T),
    aboost_d = sd(a_d/v_d, na.rm=T),
    aboost_q = sd(a_q/v_q, na.rm=T),
    aboost_i = sd(a_i/v_i, na.rm=T),
    aboost_s = sd(a_s/v_s, na.rm=T),
    aboost_r = sd(a_r/v_r, na.rm=T),
    aboost_n = sd(a_n/v_n, na.rm=T),
    aboost_op = sd(a_y_op/v_y_op, na.rm=T),
    comp = "sd_aboost") %>% 
  mutate_if(is.numeric, funs(round(., 2)))
#need to combine mean and sd into a nice single table; ask Shannon/Andrei
aboost_mean %>% as.data.frame()
aboost_sd %>% as.data.frame()


aboost_timemin<- round(mean(aboost_mean$aboost_min))
aboost_timemin_nosil<- round(mean(aboost_mean$aboost_awakemin))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
wsix_wsev_sigps <- ifelse(count(wsixs %>% filter(pval_adj<.05))==count(wsevens %>% filter(pval_adj<.05)), 
                          count(wsixs %>% filter(pval_adj<.05)), "FIXTHIS")
tau_six_d <- round(subset(csix_taus_sig,comp=="c6_d")$estimate,2)
tau_six_q <- round(subset(csix_taus_sig,comp=="c6_q")$estimate,2)
tau_six_i <- round(subset(csix_taus_sig,comp=="c6_i")$estimate,2)
tau_sev_min <- round(min(cseven_taus_sig$estimate),2)
tau_sev_max <- round(max(cseven_taus_sig$estimate),2)
csix_taus_pval <- ifelse(sum(csix_taus_sig$pval_adj>0.05)==0, "all 3 adjusted-p<.05", "FIXTHIS")
csev_taus_pval <- ifelse(sum(cseven_taus_sig$pval_adj>0.05)==0, "all adjusted-p<.05", "FIXTHIS")

```

To examine how the video data ‘scale’ to day-length data descriptively, we divided the audio count metrics by the video count metrics for each child, to derive 'audio-boost' scores for each of the 12 measures. This computation shows that the audio recordings were ~`r aboost_timemin`x longer than the video recordings, or `r aboost_timemin_nosil`x longer if only 'non-silent' portions of the recording are included. However, rather than showing a concomitant 10-fold increase in our derived count metrics (as would be expected if the video captured a 'typical' or 'representative' hour of the day), the boost was closer to fivefold across measures; see table XX. This suggests that the video recordings, by and large, had a denser concentration of nouns across our count based metrics than did the audio recordings. 

Notably, 'zero' values (e.g. recordings in which there were no nouns heard in singing) were omitted from the audio-boost computations given that they result in undefined values for a given child in a given month. The majority of variables had at least one such value, with over 1/3 of video recordings lacking instances of nouns heard in singing, reading, or by fathers each month; see Table X.

```{r propna_missing_tables, echo = F, warning = F, message = F}
#need to ask Shannon/Andrei to draft supplementals
# prop of kids with NAs for each cat, each month
propkids_with_NAs <- sixseven_spreadAV %>% 
  dplyr::select(subj, month,
                a_numtypes, v_numtypes, a_numtokens, v_numtokens, a_numspeakers, v_numspeakers,a_MOT, v_MOT, a_FAT, v_FAT, a_d, v_d, a_q, v_q, a_i, v_i, a_s, v_s, a_r, v_r, a_n, v_n, a_y_op, v_y_op) %>% 
  mutate_if(is.numeric, funs(na_if(., 0)))  %>% 
  group_by(month) %>% 
  #dplyr::select(a_numtypes: v_y_op) %>% 
  summarise_if(is.numeric, funs(round(sum(is.na(.))/44,2))) %>% 
  dplyr::select(month, v_MOT, a_FAT, v_FAT, v_q, v_i, a_s, v_s, a_r, v_r, v_n)

# prop of kids with NAs for each cat, across both months
vars_with_NAs <- sixseven_spreadAV %>% 
  dplyr::select(subj,
                a_numtypes, v_numtypes, a_numtokens, v_numtokens, a_numspeakers, v_numspeakers,a_MOT, v_MOT, a_FAT, v_FAT, a_d, v_d, a_q, v_q, a_i, v_i, a_s, v_s, a_r, v_r, a_n, v_n, a_y_op, v_y_op) %>% 
  group_by(subj) %>% 
  summarise_if(is.numeric, funs(sum)) %>% 
  mutate_if(is.numeric, funs(na_if(., 0))) %>%
  summarise_if(is.numeric, funs(round(sum(is.na(.))/44,2)))%>% 
  dplyr::select_if(any_vars(.>0))
propkids_with_NAs
vars_with_NAs
```

In order to compare the derived count metrics in our audio and video recordings directly, we next normed our count values by the number of minutes in each. For example, if an infant heard 500 noun-tokens in her 800 minutes of non-silent audio-recording, and 200 in her 60 minute video-recording, this was converted to .62 (audio) vs. 3.3 (video) noun-tokens per minute. This allows us to retain zero values omitted for the audio-boost scores above, rendering results that are more readily interpretable across our count and proportional measures.  We return to how it is best to account for unattested low-frequency events in corpora in the discussion, and provide the analagous normed analyses with zero values removed in the supplemental materials. 

With the normed data, we found identical patterns when looking within month six and within month seven: `r wsix_wsev_sigps`/12 of our count-based metrics (in each month) occurred at significantly lower rates in audio recordings than video recordings (adjusted-p<.05). The three that were statistically indistinguishable were nouns/minute produced (1) by fathers, (2) in reading, and (3) in singing (all adjusted-p>.05; these are the same measures with a large number of zero values; see table XX.)

In contrast, the correlations showed a more mixed pattern: in month six, audio vs. video normed count data only correlated significanly for 3/12 metrics, which were all utterance-type measures: number of declaratives (tau = `r tau_six_d`), questions (tau = `r tau_six_q`), and imperatives (tau = `r tau_six_i`; `r csix_taus_pval`). For month seven, 11/12 metrics correlated in audio vs. video data; number of nouns per minute heard in singing did not (excluding singing, `r tau_sev_min` - `r tau_sev_max`, `r csev_taus_pval`). See table XX and figure YY. 

```{r gr_derived_counts_diff, echo = F, warning = F}
gr_countvals_long_norm

```

```{r gr_derived_counts_corr, echo = F, fig.width=12,  fig.height= 3, warning = F}

gr_count_cor_VA_facetmonth_norm

```


```{r derived_props, echo = F, warning = F, message = F}
props_sixsev_ps <- ifelse(sum(pwas$pval_adj<0.05)+sum(pwvs$pval_adj<.05)==0, "all adjusted-p>.05","FIXTHIS")
sig_pcas <- sum(pcas$pval_adj<.05)
pcas_min <- round(min(pca_taus_sig$estimate),2)
pcas_max <- round(max(pca_taus_sig$estimate),2)
pcv_MOT <- round(subset(pcvs, comp=="pcv_MOT")$estimate,2)
pcv_FAT <- round(subset(pcvs, comp=="pcv_FAT")$estimate,2)
```

##Derived Proportions, Month 6 vs. 7.
Turning to the 10 proportion-based measures, within recording type the differences month-to-month were small. Indeed, as with the count measures, there were no significant differences between month six and seven within audio or within video recordings (`r props_sixsev_ps`). The pattern of correlations differed somewhat from the derived counts: for the audio recordings, `r sig_pcas`/10 proportional measures correlated from month 6 to month 7 (for these seven measures: Kendall’s tau range: `r pcas_min`-`r pcas_max`, adjusted-p<.05; for object co-presence, questions, and short-phrases adjusted-p>.05). For video data, only proportion of input from mom and from dad correlated significantly from month 6 to month 7 (Kendall’s tau = `r pcv_MOT` and `r pcv_FAT`, respectively; adjusted-p<.05). Thus, overall, at the group level, the proportional metrics were very stable month-to-month within recording type, but the correlations between the proportional measures across children at month six and seven were variable, especially for video-recordings.

```{r gr_derived_props, echo = F, fig.width=12, fig.height = 5, warning = F}
gr_propvals_long
gr_prop_cor_67_facetav

```

```{r propvals_countvals_figs, echo=F, message = F, warning = F}
aboost_mom7 <- propvals_mean_spreadAV %>%
  filter(prop_meas=="prop_mom" & month=="07") %>%
  dplyr::select(a_boost) %>%
  ungroup() %>%
  summarise(round(mean(a_boost),2))

aboost_dad7 <- propvals_mean_spreadAV %>%
  filter(prop_meas=="prop_dad" & month=="07") %>%
  ungroup() %>%
  dplyr::select(a_boost) %>%
  summarise(round(mean(a_boost),2))

aboost_propop <- propvals_mean_spreadAV %>%
  filter(prop_meas=="prop_op") %>%
  ungroup() %>%
  dplyr::select(a_boost) %>%
  summarise(round(mean(a_boost),2))

ttr_vid <- propvals_mean_spreadAV %>%
  filter(prop_meas=="type_token_ratio") %>%
  ungroup() %>%
  dplyr::select(video) %>%
  summarise(round(mean(video),2))
ttr_aud <- propvals_mean_spreadAV %>%
  filter(prop_meas=="type_token_ratio") %>%
  ungroup() %>%
  dplyr::select(audio) %>%
  summarise(round(mean(audio),2))
aboost_propd <- propvals_mean_spreadAV %>%
  filter(prop_meas=="propd") %>%
  ungroup() %>%
  dplyr::select(a_boost) %>%
  summarise(round(mean(a_boost),2))
aboost_propq <- propvals_mean_spreadAV %>%
  filter(prop_meas=="propq") %>%
  ungroup() %>%
  dplyr::select(a_boost) %>%
  summarise(round(mean(a_boost),2))

propwsixs_numsigdif <- sum(propwsixs$pval_adj<.05)
# propwsixs_est <- filter(propwsixs,pval_adj<.05) %>% 
#   dplyr::select(estimate) %>% abs(round(.,3))
propcsixs_sigtau<-filter(propcsixs, pval_adj<.05) %>% 
  dplyr::select(estimate) %>% 
  round(.,3)
propwsevens_numsigdif <- sum(propwsevens$pval_adj<.05)
propcsevens_sigtau<-filter(propcsevens, pval_adj<.05) %>% 
  dplyr::select(estimate) %>% 
  round(.,3)

```

##Derived Proportions, Audio vs. Video-recordings
Across recording types, proportional measures differed more substantively than count measures; see figure XX. At six months, `r propwsixs_numsigdif`/10 proportional measures differed significantly between audio and video recordings (type-token ratio, and the proportion of object presence, declaratives, and questions, all adj-p<.05), while at seven months, `r propwsevens_numsigdif`/10 did so (the same four as in month six, in addition to input from mothers and fathers; all adj-p<.05). 

Descriptively, videos featured object presence more than audio-recordings (Mdelta = `r abs(aboost_propop*100)`%), likely reflecting the less far-ranging activities families engaged in while video equipment was present. Regarding quantity, videos also had a higher type-to-token ratio (i.e. more lexical diversity; audio type-token ratio:  Mdelta = `r ttr_aud`, video type-token ratio: Mdelta = `r ttr_vid`), replicating previous work (Covington & Fall, 2010).

Across utterance-types, at a gross level, the distributions of nouns in audio and video-recordings were similar, with declaratives making up most of the noun input, followed by questions, with the remaining input spread relatively evenly across imperatives, reading, singing, and short phrases. However, audio recordings featured relatively more declaratives and fewer questions than videos (`r aboost_propd*100`, and `r abs(aboost_propq*100)`%, respectively). Finally, in month seven, mothers talked `r abs(aboost_mom7)*100`% less in audio than video, and fathers talked `r abs(aboost_dad7)*100`% more. 

```{r gr_derived_props_av, echo = F, fig.width=12, warning = F}
gr_prop_cor_VA_facetmonth

```

Turning to the correlations among proportions across recording-types, in month six only the proportion of imperatives reached significance (Kendall’s tau =`r propcsixs_sigtau`, adj-p<.05). At seven months,  three of the variables that differed significantly across recording-types also correlated significantly (proportion of noun input from fathers and mothers, and in declaratives), along with the proportion of nouns heard in reading, (all four adj-p<.05, Kendall’s tau range: `r min(propcsevens_sigtau)` - `r max(propcsevens_sigtau)`).


#Noun Frequency and Prevalence 
The results thus far indicate that across all of our proportion and count-based measures, object nouns were stable in month six and seven, but often differed across recording type (by our Wilcoxon tests). We conclude with a set of highly exploratory analyses at the word level, which aim to provide a first-pass characterization of whether audio and video recordings captured the same nouns and the same relative frequencies by examining word frequency across each month, recording type, and infant. The distribution of nouns in our recordings was zipfian: of the `r totaln_objectwords`unique object words (`r totaln_bl` lemmas) heard across months and recording types, only `r totaln_once_objectwords` (`r totaln_once_bl` lemmas) were heard more than once (see figure XX).

```{r noun_freq, echo = F, fig.width=12, fig.height = 12, warning = F, message= F}
zipf_av_67
top100_logspace_av_graph
```  

```{r top-words, warning=F, message= F, echo = F}

corAVtop67_combo_ps <- ifelse(sum(corAVtop67_combo$pval_adj>0.05)==0, "all adjusted-p<.05","FIXTHIS")
avtop100_numwords <- top100av_spread %>% nrow()
avtop100corr_est<- round(cor_AVtop$estimate,2)
avtop100corr_pval<- ifelse(cor_AVtop$p.value<.0001, "p<.0001", "fix-this")
avtop100_numwordsnozeros <- top100av_spread_nozeros %>% nrow()
avtop100corr_estnozeros <- round(cor_AVtopnozeroes$estimate,2)
avtop100corr_pvalnozeros<- ifelse(cor_AVtopnozeroes$p.value<.0001, "p<.0001", "fix-this")
```

Collapsing month, we examined the top 100 most frequent audio and video nouns (n= `r avtop100_numwords` due to ties). These words' frequencies across recording-types correlate significantly (Kendall's tau: `r avtop100corr_estnozeros`, `r avtop100corr_pvalnozeros`,) even when retaining words that only occured in one recording type (Kendall's tau: `r avtop100corr_est`, `r avtop100corr_pval`; see figure XX). Further, we find numerically stronger correlations month-to-month than across recording-types within month (month 6 audio vs. video: tau = `r round(cor_sixavtop$estimate,2)`, month 7 audio vs. video: tau = `r round(cor_sevavtop$estimate,2)`, month 6 vs. 7 audio: tau = `r round(cor_sixsevenAtop$estimate,2)`, month 6 vs. 7 video: tau = `r round(cor_sixsevenVtop$estimate,2)`, `r corAVtop67_combo_ps`; see figure XX). Thus, at the word-level too, month-to-month frequencies appear more stable than cross-recording-type frequencies.

```{r top100_corgraphs, echo = F, fig.width=12}
gr_top100_monthspread
gr_top100_avspread
#need to make a table of the top 10 av/67 words, ask Shannon/Andrei
```

Finally, looking at just the top ten words by month and recording-type, we again find greater consistency across months than recording modalities (see Figure XX and Table XX). Indeed, top words within recording-type were largely overlapping, while only two words overlapped on all four lists (book and baby). Furthermore, if instead we characterize how words were spread across infants and months, we find that the top audio words were far more common across families than the top video words were (see figure XX). Thus, daylong audio-recordings appear to render more stable high-frequency words across families, across months, than do video-recordings. 

```{r top10noun_freq, echo = F, fig.width=12, warning = F}
top10_graph
```  

